Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-25 manuscript/manuscript.Rmd
still tinkering
mini

# best constant effort based on the data on ../data/msy.csv.gz
best_action <- 0.036
msy_sim <- msy |>
    filter(action == best_action) |> 
    group_by(rep) |>
    pivot_longer(c("X", "Y", "Z"),
                names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1, policy = "msy") # natural units, policy name

>>>>

# best constant effort based on the data on ../data/msy.csv.gz
best_action <- 0.045
msy_sim <- msy |>
    filter(action == best_action) |> 
    group_by(rep) |>
    pivot_longer(c("X", "Y", "Z"),
                names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1, policy = "msy") # natural units, policy name
